Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-11 preliminaries.tex
Upload for discussion

\Ethan{Look up ``interactive protocols for BQP"}
\begin{definition}
	We say $\Pi=(P, V)$ is a protocol for the langauge $L$ with completeness error $c$ and soundness error $s$ if for all $x\in\zo^*$:
	\Ethan{TODO: errors are functions of input length}
	\begin{itemize}
		\item If $x\in L$
			$\Pr\left[(P, V)(x)=(1^n, x)\right]$
		\item TODO SOUNDNESS
	\end{itemize}
\end{definition}

\begin{definition}
	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
	We say $\Pi$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ if for all $x\in\zo^*$:
	\begin{itemize}
		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
		\item Let $(d, z)\leftarrow(P, V)(x)$. \Ethan{Same problem as last definition...} Then $d=rej$ with probability at most $c(\lambda)$.
		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x)$.
			Define $z_{ideal}$ by
			$$\begin{cases}
				z_{ideal}=\bot & \text{if } d=\Rej\\
				z_{ideal}\leftarrow D_x & \text{if } d=\Acc
			\end{cases}$$
			then $\norm{(d, z) - (d, z_{ideal})}_{TV} \leq \varepsilon$.
	\end{itemize} \hannote{need computational version of soundness?} \Ethan{Yeah. Will fix.}
\end{definition}

@@

\begin{definition}
	Let $\lambda$ be a security parameter.
	Let $(\bbP, \bbV)$ be an interactive protocol with security parameter $\lambda$.
	Then it is \emph{blind} if the following ensembles are computationally indistinguishable over $\lambda$:
	\begin{itemize}
		\item $\set{\View_{P^*}(P^*, V(x))(1^\lambda)}_{\lambda\in\bbN, x\in\zo^n}$
		\item $\set{\View_{P^*}(P^*, V(0))(1^\lambda)}_{\lambda\in\bbN, x\in\zo^n}$
	\end{itemize}
	\Ethan{Do I need to write out unrelated inputs to be fully general?}

	\Ethan{See https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf}
\end{definition}

>>>>

\Ethan{Look up ``interactive protocols for BQP"}
\begin{definition}
	We say $\Pi=(P, V)$ is a protocol for the langauge $L$ with completeness error $c$ and soundness error $s$ if for all $x\in\zo^*$ and security parameter $1^\lambda$:
	\begin{itemize}
		\item If $x\in L$, then $\Pr\left[(P, V)(x, 1^\lambda)=\Rej\right]<c(\lambda)$.
		\item If $x\notin L$, then for all cheating prover $P^*$, $\Pr\left[(P^*, V)(x, 1^\lambda)=\Acc\right]<s(\lambda)$.
	\end{itemize}
\end{definition}

\begin{definition}
	Let $\Pi=(P, V)$ be a protocol with security parameter $\lambda$ and accuracy parameter $\varepsilon=\frac{1}{\poly(\lambda)}$.
	We say $\Pi$ is a protocol for the sampling problem $(D_x)_{x\in\zo^*}$ with completeness error $c$ and computational soundness \Ethan{Specify it's computational or no?} if for all $x\in\zo^*$:
	\begin{itemize}
		\item At the end of the protocol, $V$ outputs $(d, z)$ where $d\in\set{\Acc, \Rej}$.
		\item Let $(d, z)\leftarrow(P, V)(x, 1^{1/\varepsilon}, 1^\lambda)$, then $d=\Rej$ with probability at most $c(\lambda)$.
		\item For all cheating prover $P^*$, let $(d, z)\leftarrow(P^*, V)(x, 1^{1/\varepsilon}, 1^\lambda)$.
			Define $z_{ideal}$ by
			$$\begin{cases}
				z_{ideal}=\bot & \text{if } d=\Rej\\
				z_{ideal}\leftarrow D_x & \text{if } d=\Acc
			\end{cases}$$
			then for all adversary, its probability to distinguish a sample of $(d, z)$ from that of $(d, z_{ideal})$ is less than $\varepsilon$.
	\end{itemize} \hannote{need computational version of soundness?} \Ethan{Yeah. Will fix.}
\end{definition}

@@

\begin{definition}
	Let $\lambda$ be a security parameter.
	Let $(\bbP, \bbV)$ be an interactive protocol with security parameter $\lambda$.
	Then it is \emph{blind} if the following ensembles are computationally indistinguishable over $\lambda$:
	\begin{itemize}
		\item $\set{\View_{P^*}(P^*, V(x))(1^\lambda)}_{\lambda\in\bbN, x\in\zo^n}$
		\item $\set{\View_{P^*}(P^*, V(0))(1^\lambda)}_{\lambda\in\bbN, x\in\zo^n}$
	\end{itemize}
	\Ethan{See \url{https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf}}
\end{definition}

### 2020-04-11 qpip.tex
Fix bug
Upload for discussion

@@

	Inputs: \Ethan{Should the $\SampBQP$ instance be an input?}
	\begin{itemize}
		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
		\item Error parameter $\varepsilon\in(0, 1)$
	\end{itemize}

	Ingrediants:
	\begin{itemize}
		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
		\item Let $\cVGS$ be the way to verify said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix...? How?}
	\end{itemize}

	Protocol:
	\begin{enumerate}
		\item The honest prover prepares $M=\frac{T^{21}}{\varepsilon^{33}}$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}}{\varepsilon^{15}}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $y$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{2\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ as in \Cref{cor:HamCheck} then the verifier outputs $(acc, y)$. Else, it outputs $(rej, \bot)$.
	\end{enumerate}
\end{protocol}

Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
It is simple to check that $\PiSamp$ runs in $\poly(T, \varepsilon^{-1})$ time.
We now show its completeness and soundness.
Particularly, we prove that it has $O(\varepsilon)$ soundness errors
with the understanding that by relabelling $\varepsilon'=O(\varepsilon)$ and modifying $\PiSamp$ accordingly,
one can achieve $\varepsilon'$ soundness errors while maintaining completeness and running time properties.

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and $O(\varepsilon)$ soundness error. \hannote{remind completeness and soundness with a footnote.}
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply Chernoff bound (\Cref{thm:Chernoff}) with $\mu=\frac{m}{2}$ and $\delta=\frac{c\varepsilon^2}{\left(T+\frac{T}{\varepsilon}\right)^5}$ to get
	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(\varepsilon^{-1}).$$

@@

	\Ethan{Trace out discarded copy on $\sigma'$? Or add copies on $\tau$?}

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $M$-fold tensor products of identical copies of some states $\tau_j$.
	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes M}$
	such that for all quantum-classical channels $\Lambda_i$ acting on registers with size of $\ket{\psi_{C'(x)}}$:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'-\rho)}
	\leq\sqrt{\frac{2m^2\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
	=O(\varepsilon).$$
	In our context, for $1\leq i\leq m$, $\Lambda_i$ corresponds to measurements chosen by $\cVGS$.
	$\Lambda_{m+1}$ is measurement on the data register of $\rho_k$.

	Now we claim that for each component $\tau_j$,
	if $\PSampstar$ had sent $\tau_j^{\otimes M}$ instead then the soundness error is $O(\varepsilon)$.
	Let $p_j$ be the probability that $\cVGS(\tau_j)=acc$, we seperate $\tau_j$ terms into two cases.

	First suppose $p_j<\frac{1}{2}-2\kappa$,
	then a standard Chernoff bound argument can be applied show that this case has negligible acceptance probabilities.
	That is, it outputs $(rej, \bot)$ with overwhelming probability, hence has negligible soundness errors.

	Now suppose $p_j\geq\frac{1}{2}-2\kappa$.
	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\tau_j$ and $\ket{\psi_{C'(x)}}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\tau_j, \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}})\geq1-\varepsilon^2.$$
	which in turn implies a lower bound on the respective trace distance:
	$$\frac{1}{2}\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_1<\varepsilon.$$
	Let $(d, y)$ be $\VSamp$'s output. Suppose $d=acc$, then $y$ would be the measurement on $\tau_j$'s data register,
	which is $\varepsilon$-close to that on $\ket{\psi_{C'(x)}}$.
	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has $1-\varepsilon$ probability to contain $C(x)$ due to the padding.
	So $y$ is $O(\varepsilon)$-close to $y_{ideal}$ when $d=acc$.
	Which implies that $(d, y)$ is $O(\varepsilon)$-close to $(d, y_{ideal})$.

	The cheating prover's strategies corresponding to $\tau_j$ all have $O(\varepsilon)$ soundness errors.
	As $\rho$ is a convex combination of these strategies, we conclude the same about it.
	Finally, as the outputs corresponding to $\sigma$ is $\varepsilon$-close to that of some $\rho$,
	by data processing inequality we conclude that $\PiSamp$ has $O(\varepsilon)$ soundness errors.
\end{prf}

>>>>

\Ethan{New changes: Re-parametrize so final error is eps. Write more details for soundness about the classical mix.}

@@

	Inputs:
	\begin{itemize}
		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
		\item Security parameter $1^\lambda$ where $\lambda\in\bbN$
		\item Accuracy parameter $1^{1/\varepsilon}$ where $\varepsilon=\frac{1}{\poly(\lambda)}$ \Ethan{This feels strange... Neither $\forall\poly$ nor $\exists\poly$ feels right.}
	\end{itemize}

	Ingrediants:
	\begin{itemize}
		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
		\item Let $T$ be the number of gates in $C$.
		\item Let $C'$ be $C$ padded with $\frac{6T}{\varepsilon}$ identity gates at the end.
		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
		\item Let $\cVGS$ be the way to verify said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix...? How?}
	\end{itemize}

	Protocol:
	\begin{enumerate}
		\item\label{step:qpip1-state-gen} The honest prover prepares $M=505\frac{T^{21}\lambda^2}{\varepsilon^{31}}$ \Ethan{I think? Double check later} copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item\label{step:qpip1-verify} The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\frac{T^{10}\lambda}{\varepsilon^{14}}$, and $k\xleftarrow{\$}[M]\setminus I$. \hannote{$\xleftarrow{\$}$ ?} \Ethan{Sample randomly from. I thought it's standard notation}
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $y_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ under the standard basis and save the outcome as $z$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Y=\sum_{i\in I} y_i$. If $Y>\frac{m}{2}-\kappa m$ where $\kappa=\frac{c\varepsilon^2}{72\left(T+\frac{T}{\varepsilon}\right)^5}$ and $c\in\bbR$ as in \Cref{cor:HamCheck} then the verifier outputs $(\Acc, z)$.
			Else, it outputs $(\Rej, \bot)$.
	\end{enumerate}
\end{protocol}

Note that $\VSamp$ only needs to apply $X$ and $Z$ measurements, and is classical otherwise.
It is simple to check that $\PiSamp$ runs in $\poly(n, \lambda)$ time. \Ethan{Right? Or just $\poly(\lambda)$?}
We now show its completeness and soundness.

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and is computationally sound.
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply Chernoff bound (\Cref{thm:Chernoff}) to get
	$$\Prob{Z>\frac{m}{2}-\varepsilon m}\leq\negl(\lambda).$$

@@

	Now we apply de Finetti's theorem (\Cref{deFinetti}) to approximate our measurement result on $\sigma$ with that of a classical mix over $M$-fold tensor products of identical copies of some states $\tau_j$.
	That is, there exists some $\rho=\sum_j w_j\tau_j^{\otimes m+1}$
	such that for all quantum-classical channels $\Lambda_i$ acting on registers with size of $\ket{\psi_{C'(x)}}$:
	$$\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+1}(\sigma'_{\leq m+1}-\rho)}
	\leq\sqrt{\frac{2m^2\left(n+T+\frac{T}{\varepsilon}\right)}{M-m}}
	\leq\frac{\varepsilon}{6}$$
	where $\sigma'_{\leq m+1}$ is the first $m+1$ registers of $\sigma'$.
	In our context, for $1\leq i\leq m$, $\Lambda_i$ corresponds to measurements chosen by $\cVGS$.
	$\Lambda_{m+1}$ is measurement on the data register of $\rho_k$.

	For each $\tau_j$, we define the distribution $(d_j, z_j)$ to correspond to $\VSamp$'s output if it were to receive $\tau_j^{\otimes M}$ from $\PSampstar$, and define $z_{j, ideal}$ accordingly.
	We claim that $(d_j, z_j)$ is $\frac{2\varepsilon}{6}$-close to $(d_j, z_{j, ideal})$.
	Let $p_j$ be the probability that $\cVGS(\tau_j)=\Acc$, and consider two cases as follows.

	First suppose $p_j<\frac{1}{2}-2\kappa$,
	then a standard Chernoff bound argument can be applied show that this case has negligible acceptance probabilities.
	That is, $(d_j, z_j)$ is $\negl(\lambda)$-close to $(\Rej, \bot)$.

	Now suppose $p_j\geq\frac{1}{2}-2\kappa$.
	By \Cref{cor:HamCheck} we have a lower bound for the fidelity between $\tau_j$ and $\ket{\psi_{C'(x)}}$:
	$$p_j>\frac{1}{2}-2\kappa\Rightarrow F(\tau_j, \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}})\geq1-\frac{\varepsilon^2}{36}.$$
	which in turn implies a lower bound on the respective trace distance:
	$$\norm{\tau_j - \ket{\psi_{C'(x)}}\bra{\psi_{C'(x)}}}_{tr}<\frac{\varepsilon}{6}.$$
	Suppose $d_j=\Acc$, then $z_j$ would be $\negl(\lambda)$-close to the measurement on $\tau_j$'s data register,
	which is $\frac{\varepsilon}{6}$-close to that on $\ket{\psi_{C'(x)}}$.
	As the clock register is traced out from $\ket{\psi_{C'(x)}}$, the data register has $1-\varepsilon$ probability to contain $C(x)$ due to the padding.
	So $z_j$ is $\frac{2\varepsilon}{6}$-close to $z_{ideal}$ when $d=\Acc$,
	which implies that $(d_j, z_j)$ is $\frac{2\varepsilon}{6}$-close to $(d_j, z_{j, ideal})$.

	Define $z_\rho$ to be the output distribution corresponding to if $\VSamp$ were to receive $\rho=\sum_j w_j\tau_j^{\otimes M}$ instead of $\sigma$ from the server,
	and define $z_{\rho, ideal}$ accordingly.
	We have $\norm{(d_\rho, z_\rho) - (d', z'_{\rho, ideal})}_{TV} < \frac{2\varepsilon}{6}$ since the same is true for all components $\tau_j$.

	As $(d, z)$ is $\frac{\varepsilon}{6}$-close to $(d_\rho, z_\rho)$ for some $\rho$ by de Finetti's theorem and data processing inequality,
	using triangle inequality we have $\norm{(d, z) - (d_\rho, z_{\rho, ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
	Hence we have $\norm{d - d_\rho}_{TV}\leq\frac{\varepsilon}{2}$, which implies $\norm{(d_\rho, z'_{\rho, ideal}) - (d, z_{ideal})}_{TV}\leq\frac{\varepsilon}{2}$.
	The conclusion then follows from triangle inequality.
\end{prf}
